Precise spiking motifs in neurobiological and neuromorphic data

### 2022-10-10 manuscript.tex
1.1

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction: Importance of precise spike timings in the brain}\label{sec:time}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Spiking neurons: integrators our synchrony detectors?}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Is there a neural code?}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
Neural activity is directly influenced by our neighboring environment, and also by internal states, which in turn allow to generate actions for survival, the ultimate determinant in the light of natural selection. A central question in neuroscience is to better understand this relationship. This is sometimes coined as ``decoding the neural code'', though this would imply that there would be a code, that is an explicit representation within the neural activity. Still, we will use that terminology in all generality. In that regard, it is known that some nervous activity is linked to a specific variable, for instance the stretch of a frog's limb (Galvani). An important characteristic of neuronal information is that it consists mainly in the transfer of action potentials, or spikes, which consist of brief electrochemical impulses that propagate along the axons of neurons. These have the particularity of being essentially binary in their amplitude (that is to say, they are prototypical, all or nothing).  The frequency of those spikes has been shown to be proportional to the stretch in the frog's limb (Adrian) , and this variable (measured in spikes per seconds, or Hertz) is believed to be the major contributor to the neural code. However, computational neuroscience models have hinted that the precise timing may play a crucial role~\citep{paugam-moisy_computing_2012}, an hypothesis which we will review in this manuscript.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction: Importance of precise spike timings in the brain}\label{sec:time}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Spiking neurons: integrators our synchrony detectors?}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Is there a neural code?}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
Neuronal activity is directly influenced by our immediate environment and by internal states, which then generate actions. These actions are essential for survival, which is determinant in the light of natural selection. A central question in neuroscience is to better understand this relationship. We sometimes use the expression "decoding the neuronal code", although this implies the existence of a code, i.e. an explicit representation within the neuronal activity. Nevertheless, we will use this terminology in all generality. In this respect, it is known that this neural activity is related to a specific variable, for example the stretching of a frog's limb (Galvani). A very important characteristic of neural activity is the fact that it consists mainly of action potentials, or spikes, which are brief (about one millisecond) electrochemical impulses that propagate along the axons of neurons. These have the particularity of being essentially binary in their amplitude (i.e. they are prototypical, all or nothing).  The frequency at which these spikes are emitted has been shown to be roughly commensurate with the stretch of the frog's limb (Adrian), and this variable (measured in spikes per second, or Hertz) is considered to be the main constituent of the neuronal code. However, computational neuroscience models have suggested that precise timing may play a crucial role~\citep{paugam-moisy_computing_2012}, a hypothesis that we will investigate in this manuscript.
